### 2014-02-27 paper/retrofit.tex
checkin wip

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, our specification language |specLang alpha
(targetLang nop) = ((iS,its), .->, erasef il)|, where |its| is a task
list containing terms from the embeddeding.
%}

@@

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
  sensitive non-interfering if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}

@@

\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2, V1, V2 member C|, if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |V1|$, and
   $|c2| |.->|^* |V2|$, then
   $|V1| \approx_{|l|} |V2|$.
\end{definition}

\begin{theorem}[Termination Insensitive Non-Interference (TINI)]
  For any label |il| and configurations |ici = iconf iSi iti|, |ici' =
  iconf iSi' (fullconf idi ili tSi' ivi')|, where |i member {1,2}|, if
   $|ic1| \approx_{|il|} |ic2|$,
   $|ic1| |.->|^* |ic1'|$, and
   $|ic2| |.->|^* |ic2'|$, then
   $|ic1'| \approx_{|il|} |ic2'|$.
\end{theorem}

>>>>

\begin{definition}[Information-flow control language]
    An information-flow control language |L| is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C -> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, we can no expand the definition for the
specification family of languages.
%
Specifically, |specLang alpha (targetLang nop) = (ifc C, ifc V, .->,
erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and $|ifc V|
= |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the type for
tasks whose expressions have been reduced to values.\footnote{
Here we abuse notation by using metavariables to describe types that
we previously, e.g., |it| for the type of task.
}
%}

@@

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| is termination
  sensitive non-interfering if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}

@@

\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}

\begin{theorem}[Sequential specification language is TINI]
For any target language |targetLang nop|, |specLang seqf (targetLang
nop)| satisfies TINI.
\end{theorem}
